---
title: "Visualization Theming"
ir:
  packages:
    - ggplot2
    - plotly
---

## Overview

This chapter demonstrates automatic adaptation of static plots and interactive HTML widgets in dark mode.

## Static Figures with `ggplot2`

Positron-style figure inversion automatically inverts and hue-rotates static images when the user switches to dark mode, preserving hue relationships while darkening the canvas.

```{r}
#| label: fig-ggplot
#| fig-cap: "Scatter plot of vehicle weight versus fuel economy (mtcars)."
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  theme_minimal(base_size = 13) +
  labs(
    title = "Vehicle Weight vs. Miles Per Gallon",
    x = "Weight (1000 lbs)",
    y = "Miles/(US) Gallon",
    color = "Cylinders"
  )
```

## Interactive Visualizations with `plotly`

Interactive Plotly widgets are styled via widget-level dark inversion filters to integrate seamlessly into dark mode without requiring separate server rerenders.

```{r}
#| label: fig-plotly
library(plotly)

plot_ly(
  iris,
  x = ~Sepal.Length,
  y = ~Petal.Length,
  color = ~Species,
  type = "scatter",
  mode = "markers"
) |>
  layout(
    title = "Iris Petal Length vs. Sepal Length"
  )
```
