---
title: "Nghiaagent Quarto Theme Showcase"
author: "Nghia Nguyen (Mitchell)"
date: today
format:
  html:
    theme:
      light:
        - flatly
        - _extensions/nghiaagent-quarto-theme/nghiaagent-quarto-theme.scss
      dark:
        - darkly
        - _extensions/nghiaagent-quarto-theme/nghiaagent-quarto-theme.scss
    respect-user-color-scheme: true
    monofont: "JetBrains Mono"
    code-fold: true
    toc: true
ir:
  packages:
    - gt
    - reactable
    - plotly
    - ggplot2
---

## Typography and Code

Theme showcase demonstrating typography, tables, and visualization styling.
Body text is styled in Satoshi with headings inheriting proportional weight.

Inline code references like `mtcars`, `Sepal.Length`, use shaded pills in JetBrains Mono.

```r
# Sample R code block in JetBrains Mono
summary(mtcars$mpg)
```

## Tables

### Static Table (`gt`)

```{r}
#| label: tbl-gt
library(gt)

head(iris, 6) |>
  gt() |>
  tab_header(
    title = "Iris morphological measurements",
    subtitle = "First 6 observations from the iris dataset"
  )
```

### Interactive Table (`reactable`)

```{r}
#| label: tbl-reactable
library(reactable)

reactable(
  head(mtcars, 8),
  searchable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE
)
```

## Visualizations

### Static Figure (`ggplot2`)

Positron-style figure inversion automatically adapts static plots in dark mode.

```{r}
#| label: fig-ggplot
#| fig-cap: "Scatter plot of vehicle weight versus fuel economy (mtcars)."
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  theme_minimal(base_size = 13) +
  labs(
    title = "Vehicle weight vs. Miles per gallon",
    x = "Weight (1000 lbs)",
    y = "Miles/(US) Gallon",
    color = "Cylinders"
  )
```

### Interactive Visualization (`plotly`)

Plotly widgets automatically adapt through widget-level dark inversion filters.

```{r}
#| label: fig-plotly
library(plotly)

plot_ly(
  iris,
  x = ~Sepal.Length,
  y = ~Petal.Length,
  color = ~Species,
  type = "scatter",
  mode = "markers"
) |>
  layout(
    title = "Iris petal length vs. sepal length"
  )
```
